---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# TBSpayRates

<!-- badges: start -->
[![R-CMD-check](https://github.com/dfo-mar-odis/TBSpayRates/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/dfo-mar-odis/TBSpayRates/actions/workflows/R-CMD-check.yaml)
<!-- badges: end -->

The goal of TBSpayRates is to extract rates of pay for public servants from the Treasury Board of Canada Secretariat and tools for project planning/salary forecasting.

## Installation

You can install the development version of TBSpayRates from [GitHub](https://github.com/) with:

``` r
# install.packages("remotes")
remotes::install_github("dfo-mar-odis/TBSpayRates")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(TBSpayRates)

SP_salaries <- get_salaries("SP")

SP_salaries
```


## Code of Conduct

Please note that the TBSpayRates project is released with a [Contributor Code of Conduct](https://dfo-mar-odis.github.io/TBSpayRates/CODE_OF_CONDUCT.html). By contributing to this project, you agree to abide by its terms.
